Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-15 talk/icooolps2011/paper.tex
small tweaks

We call the code that runs on top of an interpreter implemented with PyPy the
\emph{user code} or \emph{user program}.

@@

\subsection{Where Do All the Constants Come From}

@@

In this section we describe how the simple object model from
Section~\ref{sub:running} can be made efficient using the hints described in the
previous the section. The object model there is typical for many current
dynamic languages (such as Python, Ruby and JavaScript) as it relies heavily on
hash-maps to implement its objects.

>>>>

We call the code that runs on top of a VM implemented with PyPy the
\emph{user code} or \emph{user program}.

@@

\subsection{Where Do All the Constants Come From?}

@@

In this section we describe how the simple object model from
Section~\ref{sub:running} can be made efficient using the hints described in the
previous section. The object model there is typical for many current
dynamic languages (such as Python, Ruby and JavaScript) as it relies heavily on
hash-maps to implement its objects.
